---
title: "Histogram"
author: "George Gui"
date: "3/16/2018"
output:
  pdf_document
vignette: >
  %\VignetteIndexEntry{Histogram}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 4, fig.width = 6)
```


This file documents functions used for drawing histograms in the Price-Promotion-Analysis papers. 

```{r}
if(!require(CommonFunctions)){
  devtools::install_github('georgegui/CommonFunctions')
  library(CommonFunctions)
}
library(data.table)
library(gridExtra)
```


# Basic Plot

The function will plot the median of the distribution as a vertical red line. It will also automatically asign meaningful ticks on the x-axis. The default will include 0 into the axis and will truncate the outliers. 

```{r}
iris <- data.table(iris) 
ggplot_list <- list()
```

```{r}
ggplot_list[[1]] <- PrettyPlot(iris, 'Sepal.Length', include_0 = F)
ggplot_list[[1]]
```

# Weight

```{r}
ggplot_list[[2]] <- PrettyPlot(iris, 'Sepal.Length', include_0 = F, 
                               weight = 'Sepal.Width')
ggplot_list[[2]]
```

# Adjust x-axis

We can also first specifiy X-axis and pass it to the plot function. 

```{r}
my_axis <- GenerateAxisX(iris$Sepal.Length, min_x = 4, max_x = 8, xtitle = 'Sepal Length')
ggplot_list[[3]] <- PrettyPlot(iris, 'Sepal.Length', scalex = my_axis)
ggplot_list[[3]]
```

# Two colors

```{r}
iris[, is_setosa := Species == 'setosa']

ggplot_list[[4]] <- PrettyPlot(
  iris, 'Sepal.Length', include_0 = F, x_full_range = T, 
  color_legend = 'is_setosa')
ggplot_list[[4]]
```


# Plot Together

```{r}
grid.arrange(grobs = ggplot_list)
```


